Rule learning for verification from temporal data

### 2016-09-04 Travis/secs/intro.tex
more

In our previous work we used version space learning to verify configuration files from a set of correct examples~\cite{Santolucito2016}.
The tool, ConfigC, takes examples of correct files, builds a language model, which is then used to check is new configuration files adhear to those rules.
If a file is incorrect, the tool will identify the location of error, what is incorrect.
For example, ConfigC might output \texttt{Ordering Error: Expected "extension mysql.so" before "extension recode.so"}.
We describe here this algorithm in terms of version space learning to show how clear error messages are produced with this technique.
%and show that the results are garunteed to be complete.

>>>>

In our previous work we used version space learning to verify configuration files from a set of correct examples~\cite{Santolucito2016}.
The tool, ConfigC, takes examples of correct files, builds a language model, which is then used to check if new a configuration file adhears to those rules.
If a file is incorrect, the tool will identify the location of error, and tell the user what why it is incorrect.
For example, ConfigC might output \texttt{Ordering Error: Expected "extension mysql.so" before "extension recode.so"}.
We describe here this algorithm in terms of version space learning to show how clear error messages are produced with this technique.
%and show that the results are garunteed to be complete.
